---
title: "NO2 and COVID-19"
author: "Alana Schreibman"
date: "5/27/2021"
output: 
  html_document:
    toc: true
    toc_float: 
        collapsed: true
        smooth_scroll: true
    depth: 3 
    theme: cosmo
    highlight: pygments
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r, eval = TRUE}
#Load libraries needed. 
library(raster)
library(maptools)
library(ggplot2)
library(cowplot)
library(dplyr)
library(sp)
library(sf)
library(rgdal)
library(beanplot)
```

###Merging NO2 values for US with COVID data to make final data frame. 
```{r, eval = TRUE}
#Reading in US data from Earth Engine. 
continental.US.NO2.r <- raster('continental_us.tif') %>%
  flip(direction='y')
plot(continental.US.NO2.r)

#Reading in shapefile and filtering for US only.
data(wrld_simpl)
plot(wrld_simpl) 
us.shp <- wrld_simpl[wrld_simpl$NAME=="United States", ]
plot(us.shp)

#More exploration on raster NO2 file. 
head(continental.US.NO2.r)
dim(continental.US.NO2.r)
plot(continental.US.NO2.r)
plot(wrld_simpl[wrld_simpl$NAME=="United States", ], add = TRUE)
str(continental.US.NO2.r)

#Extracting mean NO2 values for US and adding to coordinates data to make final data frame.
r.vals <- raster::extract(continental.US.NO2.r, us.shp)
r.mean <- lapply(r.vals, FUN=mean, na.rm = TRUE)
final.df <- data.frame(us.shp@data, r.mean)  
rm(r.mean, r.vals)
names(final.df)[12] <- "NO2_Concentration"
names(final.df)[5] <- "location"
head(final.df)

#Merged geospatial data set with COVID data (variables come from COVID exploratory analysis RMD file). 
covid.NO2 <- merge(owid.filtered, final.df, by = "location")
```

###Reading in world satellite data. 
```{r, eval = TRUE}
#Reading in US data from Earth Engine: attempt at world file unsuccessful (too large?). 
world.NO2.r <- raster('NO2_world.tif') %>%
  flip(direction='y')
str(world.NO2.r)
world.NO2.df <- rasterToPoints(world.NO2) %>%
  as.data.frame()
world.NO2.df

#Direct conversion from NO2 raster to data frame while filtering by shapefile. 
world.fxn <- function(x) {
  r1 <- raster(x) %>% flip(dilection='y')
  r1 <- crop(r1, extent(wrld_simpl))
  r1 <- mask(r1, wrld_simpl)
  r1 <- rasterToPoints(r1, spatial = TRUE) 
  world.sat <- data.frame(r1) %>% 
      select(!("optional")) 
  assign("world.sat", world.sat, .GlobalEnv)
  world.sat
}  #Final satellite data to use for comparison to EPA data. 
world.fxn("NO2_world_earthengine_2021_06_18_13_30_49.tif")

names(world.NO2.r)
class(world.NO2.r)
head(world.NO2.r)
tail(world.NO2.r)
dim(world.NO2.r)
plot(world.NO2.r) #not showing all data points expected
plot(wrld_simpl, add = TRUE)
```

###Reading in continent satellite data. 
```{r, eval = TRUE}
#Reading in North America data from Earth Engine.
NorthAmerica.NO2.r <- raster('NO2_NorthAmerica.tif') %>%
  flip(direction='y')
str(world.NO2.r)
NorthAmerica.NO2.df <- rasterToPoints(NorthAmerica.NO2.r) %>%
  as.data.frame()
NorthAmerica.NO2.df

#Direct conversion from NO2 raster to data frame while filtering by shapefile. 
NAmerica.fxn <- function(x) {
  r1 <- raster(x) %>% flip(dilection='y')
  r1 <- crop(r1, extent(wrld_simpl))
  r1 <- mask(r1, wrld_simpl)
  r1 <- rasterToPoints(r1, spatial = TRUE) 
  world.sat <- data.frame(r1) %>% 
      select(!("optional")) 
  assign("world.sat", world.sat, .GlobalEnv)
  world.sat
}  #Final satellite data to use for comparison to EPA data. 
world.fxn("NO2_world_earthengine_2021_06_18_13_30_49.tif")

head(NorthAmerica.NO2.r)
tail(NorthAmerica.NO2.r)
dim(NorthAmerica.NO2.r)
plot(NorthAmerica.NO2.r) #not showing all data points expected
plot(wrld_simpl, add = TRUE)
```

###Correlation analysis: United States, satellite vs. ground EPA. 
####Formatting sattelite and ground data. 
```{r, eval = TRUE}
#Getting satellite data specifically for this time frame. 
July_Oct2018.sat.r <- raster('US_NO2_2018-07-01_start.tif') %>%
  flip(direction='y')
July_Oct2018.sat.r <- crop(July_Oct2018.sat.r, extent(us.shp))
July_Oct2018.sat.r <- mask(July_Oct2018.sat.r, us.shp)

#Direct conversion from NO2 raster to data frame while filtering by shapefile. 
continental.US.fxn <- function(x) {
  r1 <- raster(x) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  r1 <- mask(r1, us.shp)
  r1 <- rasterToPoints(r1, spatial = TRUE) 
  July_Oct2018.sat <- data.frame(r1) %>% 
      select(!("optional")) %>%
      select( "y", "x", "US_NO2_2018.07.01_start")
  July_Oct2018.sat <- rename(July_Oct2018.sat, Latitude = y, Longitude = x, NO2_concentration = US_NO2_2018.07.01_start)
  assign("July_Oct2018.sat", July_Oct2018.sat, .GlobalEnv)
  July_Oct2018.sat
}  #Final satellite data to use for comparison to EPA data. 
continental.US.fxn("US_NO2_2018-07-01_start.tif")

#Selecting just latitude and longitude from data frame just made to use with Pargasite retrieval. 
US.lat.lon <- July_Oct2018.sat %>% select(c(Latitude, Longitude))
write.csv(US.lat.lon, file.path("US_ground_NO2", "US_lat_lon.csv"), row.names = FALSE) #Used to gather EPA data from Pargasite. 

#Reading in EPA data
#Problem w Pargasite: only overlapping time frame is July 2018 - October 2018 (Pargasite stops working in November 2018)
July_Oct2018.ground <- read.csv(file = './US_ground_NO2/July_Oct2018NO2.csv') %>% select(c("Latitude", "Longitude", "no2_estimate")) %>% rename(NO2_concentration = no2_estimate)
July_Oct2018.ground <- data.frame(July_Oct2018.ground)
July_Oct2018.ground #Final EPA data to use in comparison to satellite data. 

#EPA data frame changed to raster format.
July_Oct2018.ground.r <- July_Oct2018.ground %>% select(c("Longitude", "Latitude", "NO2_concentration")) %>% rasterFromXYZ() 
```

####Checking for satellite data correlation to ground data.
```{r, eval = TRUE}
#Resampling raster data to be same size for comparisons. 
July_Oct2018.sat.r.re <- July_Oct2018.sat.r %>% resample(July_Oct2018.ground.r)
plot(July_Oct2018.sat.r.re)

#Perform correlation test between satellite and ground rasters. 
cor(values(July_Oct2018.sat.r.re),
    values(July_Oct2018.ground.r),
    use = "na.or.complete")

#Linear model estimation. 
lm1 <- lm(values(July_Oct2018.sat.r.re) ~ values(July_Oct2018.ground.r))
summary(lm1)

#Local correlation estimates--shows where locally on map specific regions are positively or negatively correlated. (Getting an error: code from this website https://statnmap.com/2018-01-27-spatial-correlation-between-rasters/)
values(July_Oct2018.sat.r.re) <- 1:ncell(July_Oct2018.sat.r.re)

matrix_ground <- values(July_Oct2018.ground.r)

focal_cor <- focal(
  x = July_Oct2018.sat.r.re,
  w = matrix(1, 5, 5),
  # fun = function(x, y = temp_chl_s){ # Original
    # cor(values(y)[x, 1], values(y)[x, 2], # Original
        # use = "na.or.complete")
  # },
  fun = function(x, y = matrix_ground){ # [MW]
    cor(y[x, 1], y[x, 2], # [MW]
        use = "na.or.complete")
  },
  filename = file.path("focal_cor.tif"),
  overwrite = TRUE
)
```

####Plotting satellite vs ground data. 
```{r, eval = TRUE}
ggplot() +
    geom_raster(data = July_Oct2018.sat, aes(x = Longitude, y = Latitude, fill = NO2_concentration)) +
    scale_fill_viridis_c() +
    ggtitle("NO2 US Satellite Data, July-Oct 2018") + 
    labs(fill = "NO2 Concentration \n(mol/m^2)") +
    coord_quickmap()

ggplot() +
    geom_raster(data = July_Oct2018.ground, aes(x = Longitude, y = Latitude, fill = NO2_concentration)) +
    scale_fill_viridis_c() +
    ggtitle("NO2 US EPA Ground Data, July-Oct 2018") + 
    labs(fill = "NO2 Concentration \n(ppb)") +
    coord_quickmap()
```

###Correlation analysis: China, satellite vs. ground data. 
####Formatting sattelite and ground data to be used for correlation analysis (China only). 
```{r, eval = TRUE}
#No success in retrieving data so far. 

#Getting satellite data specifically for this time frame. 
July_Oct2018.sat.r <- raster('July2018-Oct2018.tif') %>%
  flip(direction='y')
July_Oct2018.sat.r <- crop(July_Oct2018.sat.r, extent(us.shp))
July_Oct2018.sat.r <- mask(July_Oct2018.sat.r, us.shp)
plot(July_Oct2018.sat.r)
plot(us.shp, add = TRUE)
```

###Time-analysis: NO2 changes during the COVID-19 pandemic.
####US time analysis plots. 
```{r, eval = TRUE}
#Converting before lockdown and after lockdown rasters for US to data frames.  
before.lockdown <- raster('./US_NO2_comparison/US_NO2_2020-01-19_start.tif') %>%
  flip(direction='y') %>%
  rasterToPoints(spatial = TRUE) %>%
  data.frame() 
before.lockdown <- before.lockdown %>%
  rename(c(NO2_concentration = US_NO2_2020.01.19_start, Longitude = x, Latitude = y)) %>%
  select(c("Latitude", "Longitude", "NO2_concentration"))

after.lockdown <- raster('./US_NO2_comparison/US_NO2_2020-03-19_start.tif') %>%
  flip(direction='y') %>%
  rasterToPoints(spatial = TRUE) %>%
  data.frame() 
after.lockdown <- after.lockdown %>%
  rename(c(NO2_concentration = US_NO2_2020.03.19_start, Longitude = x, Latitude = y)) %>%
  select(c("Latitude", "Longitude", "NO2_concentration"))

#Plotting before and after maps. 
p1 <- ggplot() +
  geom_raster(data = before.lockdown , aes(x = Longitude, y = Latitude, fill = NO2_concentration)) + 
  geom_polygon(data = us.shp, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  coord_quickmap(
    xlim = c(-123, -65),
    ylim = c(23, 49)
  ) + 
  labs(fill = "NO2 Concentration \n(mol/m^2)") +
  scale_fill_viridis_c(limits = c(0, 0.00015)) +
  ggtitle("US NO2 Concentrations (Sentinel Satellite) Before COVID-19 Lockdown")
  
p2 <- ggplot() +
  geom_raster(data = after.lockdown , aes(x = Longitude, y = Latitude, fill = NO2_concentration)) + 
  geom_polygon(data = us.shp, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  coord_quickmap(
    xlim = c(-123, -65),
    ylim = c(23, 49)
  ) + 
  labs(fill = "NO2 Concentration \n(mol/m^2)") +
  scale_fill_viridis_c(limits = c(0, 0.00015)) +
  ggtitle("US NO2 Concentrations (Sentinel Satellite) After COVID-19 Lockdown")

plot_grid(p1, p2, labels = "AUTO", ncol = 1)
rm(p1, p2)
```

###US time analysis.
```{r, eval = TRUE}
#Function for finding medians over each time period. 
US_NO2_median <- function(x) {
  r <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r.vals <- raster::extract(r, us.shp)
  lapply(r.vals, FUN=median, na.rm = TRUE)
}
US_NO2_median("US_NO2_2020-01-19_start.tif")
US_NO2_median("US_NO2_2020-03-19_start.tif")

#Function for finding averages over each time period. 
US_NO2_average <- function(x) {
  r <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r.vals <- raster::extract(r, us.shp)
  lapply(r.vals, FUN=mean, na.rm = TRUE)
}
US_NO2_average("US_NO2_2020-01-19_start.tif")
US_NO2_average("US_NO2_2020-03-19_start.tif")

#Boxplots: not sure why post-COVID is higher median in each case. Need to adjust for degrees of urbanization? 
US_2019_change <- function(x, y) {
  r1 <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  mask(r1, us.shp)
  r2 <- raster(paste0("./US_NO2_Comparison/", (y))) %>% flip(direction='y')
  r2 <- crop(r2, extent(us.shp))
  mask(r2, us.shp)
  s <- stack(r1, r2)
  boxplot(s, col=c('red', 'blue'), 
          main='NO2 Before and After COVID-19', 
          ylab='Date',
          names = c('2019 Jan-Mar', '2019 Mar-May'))
}
US_2019_change("US_NO2_2019-01-19_start.tif", "US_NO2_2019-03-19_start.tif")

US_2020_change <- function(x, y) {
  r1 <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  mask(r1, us.shp)
  r2 <- raster(paste0("./US_NO2_Comparison/", (y))) %>% flip(direction='y')
  r2 <- crop(r2, extent(us.shp))
  mask(r2, us.shp)
  s <- stack(r1, r2)
  boxplot(s, col=c('red', 'blue'), 
          main='NO2 Before and After COVID-19', 
          ylab='Date',
          names = c('2020 Jan-Mar', '2020 Mar-May'))
}
US_2020_change("US_NO2_2020-01-19_start.tif", "US_NO2_2020-03-19_start.tif")

US_2021_change <- function(x, y) {
  r1 <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  mask(r1, us.shp)
  r2 <- raster(paste0("./US_NO2_Comparison/", (y))) %>% flip(direction='y')
  r2 <- crop(r2, extent(us.shp))
  mask(r2, us.shp)
  s <- stack(r1, r2)
  boxplot(s, col=c('red', 'blue'), 
          main='NO2 Before and After COVID-19', 
          ylab='Date',
          names = c('2021 Jan-Mar', '2021 Mar-May'))
}
US_2021_change("US_NO2_2021-01-19_start.tif", "US_NO2_2021-03-19_start.tif")
```

####China time analysis plots. 
```{r, eval = TRUE}
China.shp <- wrld_simpl[wrld_simpl$NAME=="China", ]

#Converting before lockdown and after lockdown rasters for US to data frames.  
before.lockdown <- raster('./China_NO2_comparison/China_NO2_2019-11-23_start.tif') %>%
  flip(direction='y') %>%
  rasterToPoints(spatial = TRUE) %>%
  data.frame() 
before.lockdown <- before.lockdown %>%
  rename(c(NO2_concentration = China_NO2_2019.11.23_start, Longitude = x, Latitude = y)) %>%
  select(c("Latitude", "Longitude", "NO2_concentration"))

after.lockdown <- raster('./China_NO2_comparison/China_NO2_2020-01-23_start.tif') %>%
  flip(direction='y') %>%
  rasterToPoints(spatial = TRUE) %>%
  data.frame() 
after.lockdown <- after.lockdown %>%
  rename(c(NO2_concentration = China_NO2_2020.01.23_start, Longitude = x, Latitude = y)) %>%
  select(c("Latitude", "Longitude", "NO2_concentration"))

#Plotting before and after maps. 
p1 <- ggplot() +
  geom_raster(data = before.lockdown , aes(x = Longitude, y = Latitude, fill = NO2_concentration)) + 
  geom_polygon(data = China.shp, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  coord_quickmap() +
  labs(fill = "NO2 Concentration \n(mol/m^2)") +
  scale_fill_viridis_c(limits = c(0, 0.0005)) +
  ggtitle("China NO2 Concentrations (Sentinel Satellite) Before COVID-19 Lockdown")
  
p2 <- ggplot() +
  geom_raster(data = after.lockdown , aes(x = Longitude, y = Latitude, fill = NO2_concentration)) + 
  geom_polygon(data = China.shp, aes(x = long, y = lat, group = group), colour = "black", fill = NA) +
  coord_quickmap() +
  labs(fill = "NO2 Concentration \n(mol/m^2)") +
  scale_fill_viridis_c(limits = c(0, 0.0005)) +
  ggtitle("China NO2 Concentrations (Sentinel Satellite) After COVID-19 Lockdown")

plot_grid(p1, p2, labels = "AUTO", ncol = 1)
rm(p1, p2)
```

###China time analysis.
```{r, eval = TRUE}
#Function for finding medians over each time period. 
US_NO2_median <- function(x) {
  r <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r.vals <- raster::extract(r, us.shp)
  lapply(r.vals, FUN=median, na.rm = TRUE)
}
US_NO2_median("US_NO2_2020-01-19_start.tif")
US_NO2_median("US_NO2_2020-03-19_start.tif")

#Function for finding averages over each time period. 
US_NO2_average <- function(x) {
  r <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r.vals <- raster::extract(r, us.shp)
  lapply(r.vals, FUN=mean, na.rm = TRUE)
}
US_NO2_average("US_NO2_2020-01-19_start.tif")
US_NO2_average("US_NO2_2020-03-19_start.tif")

#Boxplots: not sure why post-COVID is higher median in each case. Need to adjust for degrees of urbanization? 
US_2019_change <- function(x, y) {
  r1 <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  mask(r1, us.shp)
  r2 <- raster(paste0("./US_NO2_Comparison/", (y))) %>% flip(direction='y')
  r2 <- crop(r2, extent(us.shp))
  mask(r2, us.shp)
  s <- stack(r1, r2)
  boxplot(s, col=c('red', 'blue'), 
          main='NO2 Before and After COVID-19', 
          ylab='Date',
          names = c('2019 Jan-Mar', '2019 Mar-May'))
}
US_2019_change("US_NO2_2019-01-19_start.tif", "US_NO2_2019-03-19_start.tif")

US_2020_change <- function(x, y) {
  r1 <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  mask(r1, us.shp)
  r2 <- raster(paste0("./US_NO2_Comparison/", (y))) %>% flip(direction='y')
  r2 <- crop(r2, extent(us.shp))
  mask(r2, us.shp)
  s <- stack(r1, r2)
  boxplot(s, col=c('red', 'blue'), 
          main='NO2 Before and After COVID-19', 
          ylab='Date',
          names = c('2020 Jan-Mar', '2020 Mar-May'))
}
US_2020_change("US_NO2_2020-01-19_start.tif", "US_NO2_2020-03-19_start.tif")

US_2021_change <- function(x, y) {
  r1 <- raster(paste0("./US_NO2_Comparison/", (x))) %>% flip(direction='y')
  r1 <- crop(r1, extent(us.shp))
  mask(r1, us.shp)
  r2 <- raster(paste0("./US_NO2_Comparison/", (y))) %>% flip(direction='y')
  r2 <- crop(r2, extent(us.shp))
  mask(r2, us.shp)
  s <- stack(r1, r2)
  boxplot(s, col=c('red', 'blue'), 
          main='NO2 Before and After COVID-19', 
          ylab='Date',
          names = c('2021 Jan-Mar', '2021 Mar-May'))
}
US_2021_change("US_NO2_2021-01-19_start.tif", "US_NO2_2021-03-19_start.tif")
```