---
title: "COVID-19 Outcomes"
author: "Alana Schreibman"
date: "5/27/2021"
output: 
  html_document:
    toc: true
    toc_float: 
        collapsed: true
        smooth_scroll: true
    depth: 3 
    theme: cosmo
    highlight: pygments
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

***

The purpose of this file is to practice applying basic R commands learned through lecture videos and perform exploratory analysis on worldwide COVID-19 data. 

```{r, eval = TRUE}
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(cowplot)
```

### Our World in Data GitHub COVID-19 outcomes
Data was read in and summarized as shown below: (current file is as of 5/31)
```{r, eval = TRUE}
owid <- read.csv(url("https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/owid-covid-data.csv"), na.strings = c("", "NA"), colClasses = c("date" = "Date"), header = TRUE)
dim(owid)
```


```{r, eval = FALSE}
head(owid)
str(owid)
summary(owid)
```

#### Full Cleaned Data Set
Data set, including possible confounders for use in later analysis, is cleaned and filtered below. 
```{r, eval = TRUE}
owid.filtered <- owid %>%
                  rename(iso.code = iso_code, totcases = total_cases, totdeaths = total_deaths, totcases.mil = total_cases_per_million, totdeaths.mil = total_deaths_per_million, pop.density = population_density, med.age = median_age, older70 = aged_70_older, gdp.cap = gdp_per_capita, card.death = cardiovasc_death_rate, diab.prev = diabetes_prevalence, fem.smokers = female_smokers, male.smokers = male_smokers) %>%
                  select(c(iso.code:totcases, totdeaths, totcases.mil, totdeaths.mil, population, pop.density, med.age, older70, gdp.cap, card.death, diab.prev, fem.smokers, male.smokers)) %>% #Renamed variables and filtered to keep only those of interest. 
                  filter(date == "2020-05-31") #Filtered out all but most recent date (most recent date is a running sum of total cases).
table(owid.filtered$continent, useNA = "ifany") #Data includes both continent and country-specific outcomes. Continent outcomes can be distinguished by "NA" in the continent column; the continent name is in the location column. 
```

More exploratory analysis of data frames:
```{r, eval = FALSE}
dim(owid.filtered)
head(owid.filtered)
tail(owid.filtered)
```

#### Continent Analysis
Data is filtered to remove entries for specific country locations and include only data that aggregates COVID-19 outcomes on a continent and world scale. 
```{r, eval = TRUE}
owid.continents <- owid.filtered %>%
                    filter(is.na(continent)) %>%
                    select(-continent) #Used missingness properties to select only continent rows and then removed continent column. 
table(owid.continents$location)
```

#### Country Analysis
Data is filtered to include only country-specific COVID-19 outcomes and exclude continent and world-wide data.  
```{r, eval = TRUE}
owid.countries <- owid.filtered %>%
                    filter(!is.na(continent)) #Removed all rows with NA for continent, leaving behind only countries. 
table(owid.countries$continent)
```

#### Tests for Missingness
```{r, eval = TRUE}
table(owid.filtered$totcases, useNA = "ifany") %>%
  tail() #No missing values for total cases column. 
table(owid.filtered$totdeaths, useNA = "ifany") %>%
  tail() #Several missing values for total deaths column. Keep this in mind when analyzing. 
which(is.na(owid.filtered$totdeaths))
#Missing countries: Butan, Cambodia, Dominica, Eritrea, Fiji, Grenada, Laos, Lesotho, Mongolia, Namibia, Saint Kitts and Nevis, Saint Lucia, Saint Vincent and the Grenadines, Seychelles, Timor, Uganda, Vatican, Vietnam.

#Missingness for confounders: 
owid.countries[!complete.cases(owid.countries), ] #Most missingness in smoking categories. 
```

#### Modified Data Frames
Filtered OWID data frames further narrowed to COVID-19 cases only, deaths only, and hospitalizations only, separated by continent and by country respectively. 
```{r, eval = FALSE}
#By continent:
select(owid.continents, c(iso.code:totcases, totcases.mil)) #COVID-19 cases by continent. 
select(owid.continents, c(iso.code:date, totdeaths, totdeaths.mil)) #COVID-19 deaths by continent. 
select(owid.continents, c(iso.code:date, hosp.patients, hosp.patients.mil)) #COVID-19 hospitalizations by continent. 

#By country:
select(owid.countries, c(iso.code:totcases, totcases.mil)) #COVID-19 cases by country. 
select(owid.countries, c(iso.code:date, totdeaths, totdeaths.mil)) #COVID-19 deaths by country. 
select(owid.countries, c(iso.code:date, hosp.patients, hosp.patients.mil)) #COVID-19 hospitalizations by country.  
```

## Case Count Plots
### Continent COVID-19 Plots
Plots for exploratory analysis comparing COVID-19 cases by continent for total cases, total cases per million people, total deaths, and total deaths per million people.
```{r, eval = TRUE}
continents1 <- owid.continents %>%
                  filter(!(location %in% c("International", "World"))) %>%
                  ggplot(aes(x = location, y = totcases)) +
                  geom_bar(stat="identity") +
                  geom_text(aes(label = totcases), vjust = -0.25, size = 3) + 
                  labs(title = "Total COVID-19 Cases by Continent") +
                  labs(x = "Continent", y = "Total COVID-19 Cases") +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1)) #Barplot of total cases by continent. 

continents2 <- owid.continents %>%
                  filter(!(location %in% c("International", "World"))) %>%
                  ggplot(aes(x = location, y = totcases.mil)) +
                  geom_bar(stat="identity") + 
                  geom_text(aes(label = totcases.mil), vjust = -0.25, size = 3) + 
                  labs(title = "Total COVID-19 Cases per Million People by Continent") +
                  labs(x = "Continent", y = "Total COVID-19 Cases per Million") +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1)) #Barplot of total cases per million by continent.

plot_grid(continents1, continents2, labels = "AUTO")

continents3 <- owid.continents %>%
                    filter(!(location %in% c("International", "World"))) %>%
                    ggplot(aes(x = location, y = totdeaths)) +
                    geom_bar(stat="identity") +
                    geom_text(aes(label = totdeaths), vjust = -0.25, size = 3) + 
                    labs(title = "Total COVID-19 Deaths by Continent") +
                    labs(x = "Continent", y = "Total COVID-19 Cases") +
                    theme(axis.text.x = element_text(angle = 45, hjust = 1)) #Barplot of total deaths by continent. 

continents4 <- owid.continents %>%
                    filter(!(location %in% c("International", "World"))) %>%
                    ggplot(aes(x = location, y = totdeaths.mil)) +
                    geom_bar(stat="identity") +
                    geom_text(aes(label = totdeaths.mil), vjust = -0.25, size = 3) + 
                    labs(title = "Total COVID-19 Deaths per Million by Continent") +
                    labs(x = "Continent", y = "Total COVID-19 Cases") +
                    theme(axis.text.x = element_text(angle = 45, hjust = 1)) #Barplot of total deaths per million by continent.

plot_grid(continents3, continents4, labels = "AUTO")
```

### Top 10 Country COVID-19 Plots
Barplots filtering out the 10 countries with the highest COVID-19 cases per million people on each continent, as well as a heatmap of all countries, are the outputs of the code below: 
```{r, eval = TRUE}
ctry.mean.cases <- owid.countries %>%
    group_by(continent) %>%
    summarise(totcases.mil = mean(totcases.mil, na.rm = TRUE)) #Mean COVID-19 cases per country, grouped by continent.
mean.cases <- function(x) {
                      ctry.mean.cases %>%
                      filter(continent == x) %>%
                      select(totcases.mil) %>%
                      as.numeric()
} #Function to produce numeric value of mean COVID-19 cases per country by continent to be used in bar graphs below. 
top.ctry.cases <- function(x) { 
                    owid.countries %>% 
                    filter(continent == x) %>%
                    arrange(desc(totcases.mil)) %>%
                    head(n=10) %>%
                    ggplot(aes(x = location, y = totcases.mil)) +
                        geom_bar(stat = "identity") +
                        geom_abline(slope=0, intercept= mean.cases(x),  col = "red", lty=2) +
                        labs(x = "Country", y = "Total COVID-19 Cases per Million People") +
                        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                        labs(title = paste0("COVID-19 Cases per Million People in ", (continent = x)))
}
for (i in c("North America", "Europe", "Asia", "Africa", "Oceania", "South America")) {
  print(top.ctry.cases(i))
} #Loops function for continents of interest. 

ctry.mean.deaths <- owid.countries %>%
    group_by(continent) %>%
    summarise(totdeaths.mil = mean(totdeaths.mil, na.rm = TRUE)) #Mean COVID-19 daeths per country, grouped by continent.
mean.deaths <- function(x) {
                      ctry.mean.deaths %>%
                      filter(continent == x) %>%
                      select(totdeaths.mil) %>%
                      as.numeric()
} #Function to produce numeric value of mean COVID-19 deaths per country by continent to be used in bar graphs below. 
top.ctry.deaths <- function(x) { 
                    owid.countries %>% 
                    filter(continent == x) %>%
                    arrange(desc(totdeaths.mil)) %>%
                    head(n=10) %>%
                    ggplot(aes(x = location, y = totdeaths.mil)) +
                        geom_bar(stat = "identity") +
                        geom_abline(slope=0, intercept= mean.deaths(x),  col = "red", lty=2) +
                        labs(x = "Country", y = "Total COVID-19 Deaths per Million People") +
                        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                        labs(title = paste0("COVID-19 Deaths per Million People in ", (continent = x)))
}
for (i in c("North America", "Europe", "Asia", "Africa", "Oceania", "South America")) {
  print(top.ctry.deaths(i))
} #Loops function for continents of interest. 
```
