---
title: "NO2 Exploratory Analysis"
author: "Alana Schreibman"
date: "6/9/2021"
output: 
  html_document:
    toc: true
    toc_float: 
        collapsed: true
        smooth_scroll: true
    depth: 3 
    theme: cosmo
    highlight: pygments
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

***

The purpose of this file is to learn Earth Engine commands through the `rgee` package and retrieve the air quality data to be used in later analysis. 

``` {r, eval = FALSE}
#Load libraries needed.  
library(raster)
library(sf)
library(rgdal)
library(ggplot2)
library(tidyr)
library(dplyr)
library(tidyverse)
library(googledrive)
library(googleCloudStorageR)
library(mapview)
library(remotes)
library(reticulate)
library(rgee)
library(lubridate)
```

###Earth Engine API setup. 
``` {r, eval = FALSE}
install_github("r-spatial/rgee")
ee_install(py_env = "rgee")
ee_install()
gcs_setup()
```

```{r, eval = TRUE}
gcs_auth("/Users/alanaschreibman/ska_2.json")
Sys.setenv("GAR_CLIENT_JSON" = "/Users/alanaschreibman/ska_2.json")
gcs_auth()
gcs_auth(email = "alanacate4444@gmail.com")
```

```{r, eval = TRUE}
ee_Initialize()
ee_Initialize(email = 'alanacate4444@gmail.com')
ee_Initialize(email = 'alanacate4444@gmail.com', drive = TRUE)
ee_Initialize(email = 'alanacate4444@gmail.com', gcs = TRUE)
```

###Experimenting with Earth Engine.
```{r, eval = TRUE}
ee_Initialize()

# Successful: Selecting an image from ee$ImageCollection. 
col.NO2<-ee$ImageCollection('COPERNICUS/S5P/NRTI/L3_NO2')
start <- ee$Date("2020-03-26")
end <- ee$Date("2021-06-07")
filter<-col$filterDate(start,end) %>%
  ee$ImageCollection$mean()
ee_print(img,clear=TRUE)

#Get more information using cat:
bandNames<-img$bandNames()
cat("Bands: ",paste(bandNames$getInfo(),"\n",collapse=" "))

b1proj<- img$select('NO2_column_number_density')$projection()
cat("B1 projection: ", paste(b1proj$getInfo(),"\n", collapse = "
"))

b1scale<-img$select('NO2_column_number_density')$projection()$nominalScale()
cat("B1 Scale: ", paste(b1scale$getInfo(),"\n", collapse = " "))

Map$setCenter(65.27,24.11, zoom = 4)
Map$addLayer(filter,visParams=list(bands = "NO2_column_number_density", min = 0,max = 0.0002, palette = c("black", "blue", "purple", "cyan", "green", "yellow", "red"), opacity=0.4), "True Color Image")
```

###Downloading data for raster package in R. 
```{r, eval = TRUE}
#US only--downloading URL for local use (not good for large files--do not use).
start_time <- Sys.time()
image1 <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$filterDate('2018-06-26', '2020-06-26')$select("NO2_column_number_density") %>%
   ee$ImageCollection$mean()
geometry <- ee$Geometry$Rectangle(
  coords = c(-170, 18, -56, 71))
geom_params <- list(
 crs = 'EPSG:4326',
 region = geometry,
 maxPixels = 1E10
)
print(geom_params)
path <- image1$getDownloadUrl(geom_params)
print(path)
end_time <- Sys.time()
end_time - start_time

#All countries using cloud storage: making into function where coordinates and country name are inputs. 
countries.NO2.fxn <- function(date.start, date.end, minx, miny, maxx, maxy, country) {
  image1 <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$filterDate(date.start, date.end)$select("tropospheric_NO2_column_number_density") %>% ee$ImageCollection$mean()
  geometry <- ee$Geometry$Rectangle(
  coords = c(minx, miny, maxx, maxy),
  scale = NULL,
  crs = 'EPSG:4326'
    )
  NO2.world.countries <- ee_image_to_gcs(
    image = image1,
    region = geometry,
    bucket = "rgee_bucket", 
    fileFormat = "GEO_TIFF",
    fileNamePrefix = paste0((country), "_NO2_", (date.start))
  )
  output1 <- NO2.world.countries$start()
  output2 <- ee_monitoring(NO2.world.countries)
  return(c(output1, output2))
} 

#Selected 10 countries for exploratory analysis. 
countries.NO2.fxn(-180, 19, -66, 71.5, "United States")
countries.NO2.fxn(72, 17, 136, 54, "China")
countries.NO2.fxn(68,  7, 97, 36, "India")
countries.NO2.fxn(6,  36, 19, 48, "Italy")
countries.NO2.fxn(-74,.5 -33, -30, 6, "Brazil")
countries.NO2.fxn(-81.5, -18, -69, 0, "Peru")
countries.NO2.fxn(34, 29, 35, 34, "Israel")
countries.NO2.fxn(-74, -55.5, -54, -20, "Argentina")
countries.NO2.fxn(-180, 42, 180, 82, "Russia")
countries.NO2.fxn(-9, 49, 2, 61, "United Kingdom")

#Selecting half world rasters to mosaic together. 
countries.NO2.fxn(-90, -90, 90, 90, "Half_World")
countries.NO2.fxn(-180, -90, 0, 90, "Left_Half_World")
countries.NO2.fxn(0, -90, 180, 90, "Right_Half_World")

#US only using cloud storage: making into function where dates are input. 
geometry <- ee$Geometry$Rectangle(
  coords = c(-130, 23, -65, 49),
  scale = NULL,
  crs = 'EPSG:4326'
    )
US.date.fxn <- function(date.start, date.end) {
  image1 <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$filterDate(date.start, date.end)$select("tropospheric_NO2_column_number_density") %>% ee$ImageCollection$mean()
  NO2.continental.US <- ee_image_to_gcs(
    image = image1,
    region = geometry,
    bucket = "rgee_bucket", 
    fileFormat = "GEO_TIFF",
    fileNamePrefix = paste0("US_NO2_", (date.start), "_start")
  )
  output1 <- NO2.continental.US$start()
  output2 <- ee_monitoring(NO2.continental.US)
  return(c(output1, output2))
} 

#China only using cloud storage: making into function where dates are input. 
geometry <- ee$Geometry$Rectangle(
  coords = c(72, 17, 136, 54),
  scale = NULL,
  crs = 'EPSG:4326'
    )
China.date.fxn <- function(date.start, date.end) {
  image1 <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$filterDate(date.start, date.end)$select("tropospheric_NO2_column_number_density") %>% ee$ImageCollection$mean()
  NO2.China <- ee_image_to_gcs(
    image = image1,
    region = geometry,
    bucket = "rgee_bucket", 
    fileFormat = "GEO_TIFF",
    fileNamePrefix = paste0("China_NO2_", (date.start), "_start")
  )
  output1 <- NO2.China$start()
  output2 <- ee_monitoring(NO2.China)
  return(c(output1, output2))
} 

#Applying function:
#Used for USA ground data to satellite comparison. 
US.date.fxn("2018-07-01", "2018-10-01") 

#Comparing satellite data with 6 selected cities:
dates.2020 <- seq(as.Date("2019-12-30"), as.Date("2020-04-05"), by=7) #List of dates starting Dec 30th 2019. 
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), -125, 45, -120, 49, "Seattle")
}  
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), 113, 30, 116, 31, "Wuhan")
} 
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), 8, 44.5, 10.5, 36, "Milan")
} 
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), -1, 51, 1, 52, "London")
} 
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), -47, -24, -45.5,-23, "SaoPaulo")
} 
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), 27, -30, 29, -25, "Johannesburg")
} 


#Time analysis: Go by first day of first lockdown order -> two months later. Then find time period of equivalent two-month length, starting before the lockdown. Apply this first to 2019, then 2020, then 2021. 

#United States: California on March 19th. 
US.date.fxn("2019-01-19", "2019-03-19") 
US.date.fxn("2019-03-19", "2019-05-19") 

US.date.fxn("2020-01-19", "2020-03-19") 
US.date.fxn("2020-03-19", "2020-05-19") 

US.date.fxn("2021-01-19", "2021-03-19") 
US.date.fxn("2021-03-19", "2021-05-19") 

#China: Hubei on Jan 23rd.
China.date.fxn("2018-11-23", "2019-01-23")
China.date.fxn("2019-01-23", "2019-03-23")

China.date.fxn("2019-11-23", "2020-01-23")
China.date.fxn("2020-01-23", "2020-03-23")

China.date.fxn("2020-11-23", "2021-01-23")
China.date.fxn("2021-01-23", "2021-03-23")

#Time series weekly analysis: test code with US. 
#Weeks defined Mondays-Sundays starting on Dec 31st 2018. 
dates.2019 <- seq(as.Date("2018-12-17"), as.Date("2019-12-29"), by=7) #List of dates starting Dec 31 2018. 

for (i in 1:length(dates.2019)) {
  US.date.fxn(as.character(as.Date(dates.2019[[i]])), as.character(as.Date(dates.2019[[i]]) + 6))
}  #Loops over all weeks of the year 2019. 

#Weeks defined Mondays-Sundays starting on Dec 30th 2019. 
dates.2020 <- seq(as.Date("2019-12-16"), as.Date("2021-01-03"), by=7) #List of dates starting Dec 30th 2019. 

for (i in 1:length(dates.2020)) {
  US.date.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6))
} #Loops over all weeks of the year 2020. 

#Time series weekly analysis: test code with China 
#Weeks defined Mondays-Sundays starting on Nov 5th 2018. 
dates.2019 <- seq(as.Date("2018-11-05"), as.Date("2019-11-10"), by=7) #List of dates starting Dec 31 2018. 
for (i in 1:length(dates.2019)) {
  China.date.fxn(as.character(as.Date(dates.2019[[i]])), as.character(as.Date(dates.2019[[i]]) + 6))
}  #Loops over all weeks of the year 2019.

#Weeks defined Mondays-Sundays starting on Dec 30th 2019. 
dates.2020 <- seq(as.Date("2019-11-04"), as.Date("2020-11-08"), by=7) #List of dates starting Dec 30th 2019. 


#Time series weekly analysis: years 2019 and 2020 for right and left halves of the world. 
for (i in 1:length(dates.2019)) {
  countries.NO2.fxn(as.character(as.Date(dates.2019[[i]])), as.character(as.Date(dates.2019[[i]]) + 6), -180, -90, 0, 90, "Left_Half_World")
}
for (i in 1:length(dates.2019)) {
  countries.NO2.fxn(as.character(as.Date(dates.2019[[i]])), as.character(as.Date(dates.2019[[i]]) + 6), 0, -90, 180, 90, "Right_Half_World")
}
for (i in 1:length(dates.2020)) {
  countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), -180, -90, 0, 90, "Left_Half_World")
}
for (i in 1:length(dates.2020)) {
countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), 0, -90, 180, 90, "Right_Half_World")
}

#ITS analysis: top 10 countries
dates.2019 <- seq(as.Date("2018-12-03"), as.Date("2020-01-05"), by=7) #List of dates starting Dec 31 2018. 
for (i in 1:length(dates.2019)) {
  countries.NO2.fxn(as.character(as.Date(dates.2019[[i]])), as.character(as.Date(dates.2019[[i]]) + 6), 12, 48, 19, 52, "Czechia")
}

dates.2020 <- seq(as.Date("2019-12-02"), as.Date("2021-01-03"), by=7) #List of dates starting Dec 30th 2019. 
for (i in 1:length(dates.2020)) {
countries.NO2.fxn(as.character(as.Date(dates.2020[[i]])), as.character(as.Date(dates.2020[[i]]) + 6), 12, 48, 19, 52, "Czechia")
}
```

###Mapping data with Earth Engine interactive maps. 
####Mapping world NO2 concentrations in 2019. 
```{r, eval = TRUE}
#Successful: world map of NO2 concentrations filtered into colored zones. March-May 2019.
NO2img <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$filterDate('2019-03-26', '2019-05-26')$select("NO2_column_number_density") %>%
  ee$ImageCollection$mean()
pal<-c('#ffffb2','#fecc5c','#fd8d3c','#f03b20','#bd0026')
Map$setCenter(2.373,48.8683,3)
map.zones<-NO2img$expression("(b('NO2_column_number_density') > 0.00015) ? 4 : (b('NO2_column_number_density') > 0.000125) ? 3 : (b('NO2_column_number_density') > 0.0001) ? 2 : (b('NO2_column_number_density') > 0.00007) ? 1 : 0"
)
Map$addLayer(map.zones,list(min=0,max=4,palette=pal,opacity=0.4),
 'NO2 concentration')
```

####Mapping world NO2 concentrations in 2020. 
```{r, eval = TRUE}
#Successful: world map of NO2 concentrations filtered into colored zones. March-May 2020.
NO2img <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$filterDate('2020-03-26', '2020-05-26')$select("NO2_column_number_density") %>%
  ee$ImageCollection$mean()
pal<-c('#ffffb2','#fecc5c','#fd8d3c','#f03b20','#bd0026')
Map$setCenter(2.373,48.8683,3)
map.zones<-NO2img$expression("(b('NO2_column_number_density') > 0.00015) ? 4 : (b('NO2_column_number_density') > 0.000125) ? 3 : (b('NO2_column_number_density') > 0.0001) ? 2 : (b('NO2_column_number_density') > 0.00007) ? 1 : 0"
)
Map$addLayer(map.zones,list(min=0,max=4,palette=pal,opacity=0.4),
 'NO2 concentration')
```

####Mapping world population density. 
```{r, eval = TRUE}
#Successful: world map of population filtered into colored zones.
col.pop.den <- ee$ImageCollection("WorldPop/GP/100m/pop")$select("population") %>%
  ee$ImageCollection$mean()
pal<-c('#ffffb2','#fecc5c','#fd8d3c','#f03b20','#bd0026')
Map$setCenter(2.373,48.8683,3)
map.zones<-pop.den$expression("(b('population') > 40) ? 4 : (b('population') > 35) ? 3 : (b('population') > 25) ? 2 : (b('population') > 15) ? 1 : 0"
)
Map$addLayer(map.zones,list(min=0,max=4,palette=pal,opacity=0.4),
 'population density')
```

###Unsuccessful Earth Engine commands (delete later).
####Unsuccessful: playing with map settings. 
```{r, eval = TRUE}
#Can't figure out the problem here: seems like map generated is empty.
blocks <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")
start <- ee$Date("2019-07-11")
end <- ee$Date("2019-07-20")
subset <- blocks$filterDate(start,end)
image <- subset$first()
image
sf_subset <- ee_as_sf(x = image)
no2viz <- list(
        min = 0,
        max = .0002,
        bands = "NO2_column_number_density",
        palette = c("black", "blue", "purple", "cyan", "green", "yellow", "red")
)
Map$addLayer(image, no2viz,'NO2')
```

###Unsuccessful: time series analysis.
```{r, eval = TRUE}
#Goal: Filter the dataset by dates, reproject and select only the band "NO2_column_number_density". Get a time series plot of NO2 values. 
#Problem here: "request payload size exceeds the limit: 10485760 bytes" error message. 
NO2 <- ee$ImageCollection("COPERNICUS/S5P/NRTI/L3_NO2")$
  filterDate("2019-04-01","2020-04-01")$
  map(function(x) x$reproject("EPSG:4326")$select("NO2_column_number_density"))
world.sf <- st_read("world_maps/country_gen_trim.shp")  # Read shapefile as an sf object
world.geo <- st_geometry(world.sf)

ee__NO2 <- ee_extract(NO2, world.geo, sf = FALSE)
colnames(ee_NO2) <- sprintf("%02d", 1:12)
ee_NO2$name <- nc$NAME

ee_NO2 %>%
  pivot_longer(-name, names_to = "month",values_to = "NO2_column_number_density")%>%
  ggplot(aes(x = month, y = NO2_column_number_density, group = name, color = NO2_column_number_density)) +
      geom_line(alpha = 0.4)+
      xlab("Month") +
      ylab("NO2 Concentration") +
      theme_minimal()
```

###Unsuccesul: time band with linear fit
```{r, eval = TRUE}
#Goal is to compute trend in NO2 levels over the years and perform a linear fit. Problem: output map seems empty. 
createTimeBand <-function(img) {
  year <- ee$Date(img$get('system:time_start'))$get('year')$subtract(2018L)
  ee$Image(year)$byte()$addBands(img)
}
collection <- ee$
  ImageCollection('COPERNICUS/S5P/NRTI/L3_NO2')$
  select('NO2_column_number_density')$
  map(createTimeBand)
col_reduce <- collection$reduce(ee$Reducer$linearFit())
col_reduce <- col_reduce$addBands(
  col_reduce$select('scale'))
ee_print(col_reduce)
Map$setCenter(9.08203, 47.39835, 3)
Map$addLayer(
  eeObject = col_reduce,
  visParams = list(
    bands = c("scale", "offset", "scale"),
    min = 0,
    max = c(0.5, 5, -0.5)
  ),
  name = "NO2 trend"
)
```
